\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 12 -- Group 2}
\author{Location: 6 B 0}
\date{16th May 2019, 12:30--14:00}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Chair)(Minutes),
Peter Galea St John,
Matthew Vella,
Neil Vassallo.

%\section*{Apologies}
% Members with a justifiable excuse - remove section if there were none
%Richard Bradford

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item Progress report from group members:
   \begin{enumerate}
   \item Finished saving and loading to EEPROM.
  
   \end{enumerate}


\item Matters arising:
\begin{enumerate}
	\item The video was recorded.
	. \item After a small discussion, the game was changed to being fully interrupt based. An interrupt changes a flag and the screen updates as opposed to it updating on every cycle.
	\item Game is now fully playable from end to finish and without any known bugs. Also extremely more efficient due to the above change.

\end{enumerate}

\end{enumerate}


\section*{Actions}

\begin{enumerate}

\item Finish Doxygen comments[10.3]
\begin{flushright}
	Assigned to: \textbf{Aidan Cauchi} \\
	Deadline: \textbf{Wednesday 22nd May}
\end{flushright}

\item Upload digital scaling form and finish user acceptance test.[12.1]
\begin{flushright}
	Assigned to: \textbf{Peter Galea St. John} \\
	Deadline: \textbf{Wednesday 22nd May}
\end{flushright}

\item Edit and upload the video.[12.1]
\begin{flushright}
	Assigned to: \textbf{Aidan Cauchi} \\
	Deadline: \textbf{Wednesday 22nd May}
\end{flushright}

\item Ensure design brief is up to date.[12.1]
\begin{flushright}
	Assigned to: \textbf{All members} \\
	Deadline: \textbf{Wednesday 22nd May}
\end{flushright}

\end{enumerate}	

\end{document}
