\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 7 -- Group 2}
\author{Location: 6 B 0}
\date{11th April 2019, 12:30--13:30}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Chair),
Peter Galea St John,
Matthew Vella(Minutes),
Neil Vassallo.

%\section*{Apologies}
% Members with a justifiable excuse - remove section if there were none
%Richard Bradford

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item Progress report from group members:
   \begin{enumerate}
   \item The 7 segment display was interfaced with the board

   \item We managed to vary the distance of the sensor

   \item We managed to vary the distance of the sensor
	
   \item We researched more about EEPROM
	\begin{itemize}
		\item The board has 2kb of flash memory which is a small section at the beginning of the address space.
		\item Though, we have to be careful since this is where the program code gets stored. 
		\item More research is needed about how to store data to memory, perheps through libraries/help functions. 
	\end{itemize}

    \item Matters arising
	\begin{enumerate}
		\item None noted. 
	\end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Research about using NVRAM instead of SD card for persistent storage.[4.4]
\begin{flushright}
	Assigned to: \textbf{Neil Vassallo, Matthew Vella} \\
	Deadline: \textbf{Tuesday 16th April}
\end{flushright}

\item Wiring and cleaning up the code.[7.1]
\begin{flushright}
	Assigned to: \textbf{Aidan Cauchi, Peter Galea St. John} \\
	Deadline: \textbf{Tuesday 16th April}
\end{flushright}

\item Coding the seven segment display. [7.1]
\begin{flushright}
	Assigned to: \textbf{Neil Vassallo, Aidan Cauchi} \\
	Deadline: \textbf{Tuesday 16th April}
\end{flushright}

\item Finish the build of the model. [7.1]
\begin{flushright}
	Assigned to: \textbf{Matthew Vella} \\
	Deadline: \textbf{Tuesday 16th April}
\end{flushright}

\item Test proximity sensor with physical hoop. [7.1]
\begin{flushright}
	Assigned to: \textbf{Matthew Vella,  Peter Galea St. John} \\
	Deadline: \textbf{Tuesday 16th April}
\end{flushright}

\end{enumerate}	
\end{enumerate}

\end{document}
