\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 1 -- Group 2}
\author{Location: -1  B 2}
\date{28th February 2019, 12:30--13:30}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Minutes),
Peter Galea St John (Chair),
Matthew Vella (was present over voice chat due to sickness),
Neil Vassallo.

%\section*{Apologies}
% Members with a justifiable excuse - remove section if there were none
%Richard Bradford

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item Progress report from group members:
   \begin{enumerate}
   \item Matthew presented a layout for the physical model:
	\begin{itemize}
		\item Plywood 70cm by 55cm.
		\item Back court 55cm by 50cm.
		\item The board will fit underneath.
	\end{itemize}
   \item Peter presented a layout of what components would be needed:
	\begin{itemize}
		\item 2/4 7-segment display blocks for displaying time left.
		\item LCD used to display scores and main menu.
		\item Either 1 joystick or a few dedicated buttons for menu selection.
		\item (Possibility) LED's and/or speaker.
		\item For scoring in the hoop either a laser/receiver combination with a mirror opposite it or a photodiode opposite the laser where the signal gets cut off when the ball passes through the hoop or a proximity sensor (needs more testing on acceptable threshold proximity).
	\end{itemize}

   \item Aidan and Neil concluded that thinking about software is too difficult for now given that the labs haven't started yet and they don't have access to the board at home.
   \item Matthew suggested that LEDs light up and speaker plays a sound after every goal.
   \item With respect to the project design, the project can be split as follows:
	\begin{itemize}
		\item Building the actual model.
		\item Interfacing with LCD/7-segment display.
		\item Wiring/integrating components.
		\item Testing.
		\item Main menu programming.
		\item In-game programming.
		\item High score persistence.
	\end{itemize}
   \item With respect to design brief management section:
	\begin{itemize}
		\item Weekly meetings to be held every Thursday at 12:30.
		\item People taking minutes and creating agendas are to be changed/rotated every week.
		\item Goals are to be set every week keeping in mind the different tasks to be tackled (see above).
		\item The above may change depending on progress made/any unexpected problems thay may arise (ideally they don't).
	\end{itemize}
   \end{enumerate}

% Add other items here as necessary

%\item Matters arising
   %\begin{enumerate}
 %  \item First item discussed that was not on the agenda
  % \end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Povide diagram of physical model. [1.1]
\begin{flushright}
Assigned to: \textbf{Matthew Vella} \\
Deadline: \textbf{Wednesday 6th March}
\end{flushright}

\item Provide component schematics. [1.1]
\begin{flushright}
Assigned to: \textbf{Peter Galea St. John} \\
Deadline: \textbf{Wednesday 6th March}
\end{flushright}

\item Provide flowcharts of program logic. [1.1]
\begin{flushright}
Assigned to: \textbf{Aidan Cauchi} \\
Deadline: \textbf{Wednesday 6th March}
\end{flushright}

\item Compiling design brief with provided diagrams and writing the other sections. [1.1]
\begin{flushright}
Assigned to: \textbf{Neil Vassallo} \\
Deadline: \textbf{Wednesday 6th March}
\end{flushright}

\item Get acquainted with the manuals provided. [1.1]
\begin{flushright}
Assigned to: \textbf{All members} \\
Deadline: \textbf{Next meeting (7th March)}
\end{flushright}

\end{enumerate}

\end{document}
