\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 4 -- Group 2}
\author{Location: 8 B 0}
\date{21st March 2019, 12:30--13:30}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Minutes),
Peter Galea St John,
Matthew Vella (Chair).

\section*{Apologies}
%Members with a justifiable excuse - remove section if there were none
Neil Vassallo (Sick)

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item As Neil was absent, minutes were taken by Aidan instead.

\item Progress report from group members:
   \begin{enumerate}
   \item Matthew:
	\begin{itemize}
		\item  The material was bought and the wood was pencil marked according to our design. The glue was also bought but the design was not started yet as discussed with the group so that if minor or major changes are made to our primary concept, they can be applied.
	\end{itemize}
   \item Aidan:
	\begin{itemize}
		\item More research was carried out on how to interface with peripherals. Focus was shifted more on how to use the pins of the board to connect any peripheral rather than the joystick itself. This shift in focus should help with interfacing a range of devices. Considerable progress was made but more time is needed to figure out how to configure the fixed adresses and read inputs from said pins.
	\end{itemize}
\item Peter:
	\begin{itemize}
		\item Briefly demonstrated how wiring certain components would work.
		\item Told team about HR0214-100A IR Proximity sensor. Ideal due to low delay time and configurable sensing distance. Still have to confirm compatibility with the board.
	\end{itemize}

   \end{enumerate}

% Add other items here as necessary

\item Matters arising
   \begin{enumerate}
   	\item Discussed using NVRAM instead of SD card as suggested in feedback form.
	\item Try to look into using timer interrupts rather than poll the timer each time (as suggested in feedback form).
   \end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Buy balls, basketball net and board mountings for wood based flooring. [4.1]
\begin{flushright}
Assigned to: \textbf{Matthew Vella} \\
Deadline: \textbf{Thursday 28th March}
\end{flushright}

\item Confirm whether proximity sensor is compatible with board. [4.1]
\begin{flushright}
Assigned to: \textbf{Peter Galea St. John} \\
Deadline: \textbf{Thursday 28th March}
\end{flushright}

\item Research about using NVRAM instead of SD card for persistent storage. [4.1]
\begin{flushright}
	Assigned to: \textbf{Neil Vassallo} \\
	Deadline: \textbf{Thursday 28th March}
\end{flushright}

\item Figure out how to access the board pins through software for interfacing with peripherals. [4.1]
\begin{flushright}
	Assigned to: \textbf{Aidan Cauchi} \\
	Deadline: \textbf{Thursday 28th March}
\end{flushright}

\item Testing components and interfacing LCD display. [2.3]
\begin{flushright}
Assigned to: \textbf{Peter Galea St. John} \\
Deadline: \textbf{Thursday 28th March}
\end{flushright}

\end{enumerate}


\end{document}
