\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 6 -- Group 2}
\author{Location: 6 B 0}
\date{4th April 2019, 12:30--13:30}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Chair),
Peter Galea St John (Minutes),
Matthew Vella,
Neil Vassallo.

%\section*{Apologies}
% Members with a justifiable excuse - remove section if there were none
%Richard Bradford

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item Progress report from group members:
   \begin{enumerate}
   \item Interfacing with E18 d80nk IR proximity sensor was completed
	\begin{itemize} 
		\item Requirements:
		\begin{itemize}
			\item Black wire was connected to pin 16.
			\item Blue wire was connected to ground.
			\item Brown wire was connected to 5 V.
		\end{itemize}
	\end{itemize}
   \item Menu was set up with three options:
	\begin{itemize}
		\item a. Play Game.
		\item b. Settings.
		\item c. High Scores.
	\end{itemize}
	\item Matters arising
	\begin{enumerate}
		\item None noted. 
	\end{enumerate}

	\end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Research about using NVRAM instead of SD card for persistent storage.[4.3]
\begin{flushright}
	Assigned to: \textbf{Neil Vassallo, Matthew Vella} \\
	Deadline: \textbf{Thursday 11th April}
\end{flushright}

\item Figure out how to connect and interface the seven segment boards with board. [6.1]
\begin{flushright}
	Assigned to: \textbf{Aidan Cauchi, Peter Galea St. John} \\
	Deadline: \textbf{Thursday 11th March}
\end{flushright}
	
\end{enumerate}

\end{document}
