\documentclass[11pt,a4paper]{article}

\title{ Minutes for meeting 8 -- Group 2}
\author{Location: 6 B 0}
\date{18th April 2019, 12:30--14:00}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Aidan Cauchi (Chair)(Minutes),
Peter Galea St John,
Matthew Vella,
Neil Vassallo.

%\section*{Apologies}
% Members with a justifiable excuse - remove section if there were none
%Richard Bradford

%\section*{Absent}
% Members without a justifiable excuse - remove section if there were none
%Robert De Niro

\section*{Discussion}

\begin{enumerate}

% There should be an item corresponding to each of the agenda items for this
% meeting.

\item Minutes from the previous meeting were read and approved.

\item Progress report from group members:
   \begin{enumerate}
   \item Managed to save to EEPROM.
   \item Model was built.
   \end{enumerate}

\item Matters arising:
\begin{enumerate}
	\item Decided that one screen would be best as it would get rid of a lot of wiring issues.
	\item Changed the location of the microcontroller on the model to the front instead of the back.
	\item Decided to use the LCD supplied with the board as the one screen.
\end{enumerate}

\end{enumerate}


\section*{Actions}

\begin{enumerate}

\item Test sensor with interrupts [8.1]
\begin{flushright}
	Assigned to: \textbf{All members} \\
	Deadline: \textbf{Thursday 25th April}
\end{flushright}

\item Decide on where to put sensor and hoop.[8.1]
\begin{flushright}
	Assigned to: \textbf{Peter Galea St. John, Matthew Vella} \\
	Deadline: \textbf{Thursday 25th April}
\end{flushright}

\item Discuss starting to upload project to SVN [8.1]
\begin{flushright}
	Assigned to: \textbf{All members} \\
	Deadline: \textbf{Thursday 25th April}
\end{flushright}

\end{enumerate}	

\end{document}
